Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2016-01-04 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
remove TODO for improving slanted cell figure

Cut cell grids are generated in a different way to the typical shaving technique described by \citet{adcroft1997}.  Starting from a uniform grid, all cell vertices that lie beneath the orography are moved up to the surface.  Additionally, to avoid creating very thin cells, all vertices up to $\Delta z/5$ above the orography are moved down to the surface.  \TODO{should I include an illustration of how this extra tweak helps?  can I incorporate it into the existing figure?  yes, by adding a row above the existing top row, and moving the rightmost terrain point closer to the upper right vertex in $c_2$} Where all four of a cell's vertices are moved, the cell has zero volume and so it is removed.  Where two vertices at the same horizontal location are moved up to the surface they will occupy the same point; this results in a zero-length edge that is removed to create a triangular cell.  Figure~\ref{fig:grid-generation} shows how a $2 \times 2$-cell, uniform grid is transformed into a cut cell grid.  Cell $c_4$ is removed because it has zero volume, and the zero-length edge at point $p$ is removed to create a triangular cell, $c_3$.

>>>>

Cut cell grids are generated in a different way to the typical shaving technique described by \citet{adcroft1997}.  Starting from a uniform grid, all cell vertices that lie beneath the orography are moved up to the surface.  Additionally, to avoid creating very thin cells, all vertices up to $\Delta z/5$ above the orography are moved down to the surface.
Where all four of a cell's vertices are moved, the cell has zero volume and so it is removed.  Where two vertices at the same horizontal location are moved up to the surface they will occupy the same point; this results in a zero-length edge that is removed to create a triangular cell.  Figure~\ref{fig:grid-generation} shows how a $2 \times 2$-cell, uniform grid is transformed into a cut cell grid.  Cell $c_4$ is removed because it has zero volume, and the zero-length edge at point $p$ is removed to create a triangular cell, $c_3$.
